---
title: "The Various Factors That Affect Sleep Patterns"
author: "Dhruv Ashok, Kai Magbuhat, Nikhila Suneel"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
source("../source/chart_3.R")
source("../source/summary_info.R")
source('../source/chart_2.R")

```

## Summary Paragraph
The chosen subset of the study comparing sleep to screen time in children contained `r summary_info$num_observations` observations with `r summary_info$num_variables` variables. The study collected data on a variety of chidren, ranging from age `r summary_info$min_age` to age `r summary_info$max_age`. While Chart 1 displays the general correlation between sleep time per night and screen time per day, we may observe some general statistics about the distribution of sleep and screen times.
The average number of hours spent sleeping every night across children of all sexes and ages is `r summary_info$avg_sleep`, and the median is `r summary_info$median_sleep`. Thus, the sleep distribution is `r get_skew(summary_info$avg_sleep, summary_info$median_sleep)` skewed.
In addition, the average number of hours of screen time every day across children of all sexes and ages is `r summary_info$avg_screen_time`, and the median is `r summary_info$median_screen_time`. Thus, the screen time distribution is `r get_skew(summary_info$avg_screen_time, summary_info$median_screen_time)` skewed.

## Summary Table
[table goes here]


## Charts
### Chart 1
### Chart 2
### Chart 3
```{r bar_chart, echo=FALSE}
bar_chart
```
```{r histogram_chart, echo=FALSE}
histogram_chart
```

This grouped bar chart compares the average sleep duration in hours, by age group, for patients with a diagnosed form of depression (the condition group) and those without a diagnosed form of depression (the control group). The chart was included to determine if there was a correlation between diagnosed depression and sleep duration. We can observe from the chart that, while not true for every age group in this study, for the *majority* of age groups the condition group gets _**less**_ sleep on average compared to the control group. Further statistical analysis or studies may need to be conducted to determine if this correlation is signficant, and there are some data quality issues as there was no data for the control group for the 55-59 age group. Still, this correlation can certainly be explored further.

The grouped histogram chart is comparing multiple variables. It includes snoring range, respiration rate, hours of sleep, blood oxygen, heart rate, eye movement, limb movement rate, body temperature, and stress state. These patients were tested with all of these variables and then tested for hours of sleep and varying ranges of rate movements. I included in the chart multiple charts of each variables. Each chart reveals information on the data points
from all 600 observations for that variable. Some notable observations is that respirtation rate was more trending towards the lower end of bmp. For body temperature the data points trended towards the higher end of degrees. The variable of blood oxygen ranges is trending more towards the higher end of 90. 
The distribution of data points from this chart can be explored more. 
